
\begin{thebibliography}{9}


\thispagestyle{numberingStyle}
\pagestyle{numberingStyle}


\bibitem{htmlcssjs} 
J. Meloni, \textit{HTML5, CSS3 y JavaScript}, 2nd ed. Madrid: Anaya Multimedia, 2015.

\bibitem{spring}
``spring.io", Spring.io, 2018. [Online]. Available: https://spring.io/. [Accessed: 04- Jun- 2018].

\bibitem{jpa}
M. Keith and M. Schnicariol, \textit{Pro JPA 2}. New York: Apress, 2009.

\bibitem{jaxrs} 
B. Burke, \textit{RESTful Java with JAX-RS 2.0}, 2nd ed. Sebastopol: O'Reilly, 2013.

\bibitem{thymeleaf}
``Thymeleaf", Thymeleaf.org, 2018. [Online]. Available: https://www.thymeleaf.org/. [Accessed: 04- Jun- 2018].

\bibitem{jquery}
J. js.foundation, ``jQuery", Jquery.com, 2018. [Online]. Available: https://jquery.com/. [Accessed: 02- Jun- 2018].

\bibitem{bootstrap}
a. Mark Otto, ``Bootstrap", Getbootstrap.com, 2018. [Online]. Available: https://getbootstrap.com/. [Accessed: 02- Jun- 2018].


\bibitem{ajax} 
M. Firtman, \textit{Ajax}, 2nd ed. Barcelona: Marcombo, 2011.

\bibitem{maven}
B. Porter, J. Zyl and O. Lamy, ``Maven – Welcome to Apache Maven", Maven.apache.org, 2018. [Online]. Available: https://maven.apache.org/. [Accessed: 04- Jun- 2018].


\bibitem{git}
``Git", Git-scm.com, 2018. [Online]. Available: https://git-scm.com/. [Accessed: 02- Jun- 2018].

\bibitem{tomcat}
A. Project, ``Apache Tomcat® - Welcome!", Tomcat.apache.org, 2018. [Online]. Available: http://tomcat.apache.org/. [Accessed: 04- Jun- 2018].

\bibitem{ionic} 
A. Ravulavaru and M. Hartington, \textit{Learning Ionic : Build real-time and hybrid mobile applications with Ionic}. Birmingham, England: Packt Publishing, 2015.

\bibitem{ionic2}
``Build Amazing Native Apps and Progressive Web Apps with Ionic Framework and Angular", Ionic Framework, 2018. [Online]. Available: https://ionicframework.com/. [Accessed: 02- Jun- 2018].

\bibitem{rup} 
I. Jacobson, G. Booch and J. Rumbaugh, \textit{El proceso unificado de desarrollo de software}. Madrid: Addison Wesley, 2000.

\bibitem{patterns} 
E. Gamma, \textit{Design patterns}. Reading, Mass.: Addison-Wesley, 1995.



\end{thebibliography}
\addcontentsline{toc}{chapter}{Bibliografía}

